%------------------------
% Ethan's Résumé Template
% Author: necusjz
% License: CC-BY-4.0
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{bm}
\usepackage{marvosym}
\usepackage{multicol}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{hyperref}
\definecolor{lightblue}{RGB}{173, 216, 230} 
\hypersetup{
    colorlinks = true,  
    urlcolor   = blue,  
}
\setlength{\multicolsep}{0pt}
\input{glyphtounicode}

% font options
\usepackage{newpxtext}
\linespread{1.05}  
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}



\definecolor{mypink}{RGB}{255,192,203} 
\definecolor{mydarkred}{RGB}{139,0,0}  
\newcommand{\myhighlight}[1]{%
  \colorbox{mypink}{\textcolor{mydarkred}{\textbf{#1}}}%
}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


% subsection formatting
\titleformat{\subsection}{
  \vspace{-2pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
% ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\twopartheader}[2]{
  \vspace{-2pt}\noindent
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}[label=\textopenbullet]\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1}}\hfill
  \foreach \x in {1,...,5}{%
    \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}


% =======================begin==============================
\begin{document}

% contact information
\begin{center}
  \textbf{\LARGE\scshape Xiyuan Yang} \\
  \vspace{1pt}\small
  \href{mailto:yangxiyuan@sjtu.edu.cn}{yangxiyuan@sjtu.edu.cn}
  $\ \diamond\ $
  Shanghai Jiao Tong University
  $\ \diamond\ $
  Shanghai, China
  \\
  GitHub: \href{https://github.com/xiyuanyang-code}{https://github.com/xiyuanyang-code}
  \\
  Online Resume: \href{https://xiyuanyang-code.github.io/cv}{https://xiyuanyang-code.github.io/cv/}
\end{center}



\section{Education}
\cvheadingstart
\cvheading
{Shanghai Jiao Tong University}{Shanghai, China}
{School of Artificial Intelligence}{09/2024 - present}

\begin{multicols}{2}
GPA: \textbf{4.1}/4.3 (Ranked \textbf{2} out of 66)

Score: \textbf{93.9}/100
\end{multicols}


Scholarships: 

\begin{itemize}[nosep]
  \item National Scholarship (2025) (first \textbf{3}\%)
  \item Zhiyuan Honor Scholarship (2024, 2025)
  \item "Han Ying Ju Hua" Scholarship (2025, \textbf{15} per year.)
  \item SJTU Undergraduate Excellence Scholarship (2024)
\end{itemize}

High graded courses: 

\begin{multicols}{2}
\begin{itemize}[nosep]
  \item Comprehensive Programming: \textbf{100}
  \item Prob. and Statistics (Honor): \textbf{100}
  \item Algorithm Design: \textbf{100}
  \item Numerical Analysis: \textbf{100}
  \item Linear Algebra (Honor): 98
  \item C++ Programming Design (Honor): 98
  \item Fundamentals of Artificial Intelligence (ML, DL and RL): 98
\end{itemize}
\end{multicols}

\textbf{22} courses achieved A/A+ (\textbf{14 A+}), including \textbf{all major-related courses}.

\cvheadingend
\vspace{-5pt}

\section{Research}

My research interests lie in building \textbf{General Self-Evolving Agentic AI}, dedicated to pushing the boundaries of intelligence in large language models. 

Currently Undergraduate researcher in \textbf{MAGIC} (\textbf{M}ulti-\textbf{A}gent \textbf{G}overnance \& \textbf{I}ntelligence \textbf{C}rew), supervised by \textbf{\href{https://scholar.google.com/citations?user=W_Q33RMAAAAJ&hl=zh-CN}{Siheng Chen}}.
\newline

\textbf{InfoMosaic-Bench: Evaluating Multi-Source Information Seeking in Tool-Augmented Agents}

\myhighlight{ICLR 2026 Poster (3rd Author)}

\url{https://arxiv.org/abs/2510.02271}

Pioneered \textbf{InfoMosaic-Bench}, the first benchmark dedicated to multi-source information seeking in LLM agents, demonstrating the critical need to integrate general-purpose web search with thousands of domain-specific tools via \textbf{MCP} (Model Context Protocol). Experiments revealed that web information alone is insufficient (GPT-5 Acc: 38.2\%) for information seeking due to incorrect tool usage/selection.
\newline 

\textbf{MCP-Persona: Benchmarking LLM Agents on Personalized MCP Tools and Tasks}

\myhighlight{ICML 2026 (In Submission, Co-first author)}

Pioneered \textbf{MCP-Persona}, the first benchmark for evaluating LLM agents on \textbf{personalized} Model Context Protocol (MCP) tools. MCP-Persona captures real-world challenges of tools interacting with individual accounts and local databases across diverse platform including Reddit, Xiaohongshu, Lark, and Slack. Extensive evaluations of state-of-the-art agents reveal substantial deficiencies in personalized tool utilization.
\newline 

\textbf{AppCopilot: Toward General, Accurate, Long‑Horizon, and Efficient Mobile Agent}

\myhighlight{ICML 2026 (In Submission, Position-Track)}


\url{https://github.com/OpenBMB/AppCopilot} (\textbf{300+} stars.)

Developed \textbf{AppCopilot}, a multi-modal, multi-agent on-device assistant that addresses core challenges in the mobile-agent landscape. AppCopilot significantly improves generalization, on-screen interaction accuracy, and long-horizon task completion, while optimizing performance and efficiency on mobile devices.



\section{Technical Projects}

% ============== Project1 AlphaBuild ============== %
\textbf{AlphaBuild: Generating Formulaic Alphas on a Wider Range of Stock Data with Reinforcement Learning}

Leading AlphaBuild as the final project of course \textbf{AI1803}, an RL-based methodology using PPO to optimize factor mining process based on \href{https://github.com/RL-MLDM/alphagen}{AlphaGen}, achieving superior backtest performance by leveraging smaller, parallel factor pools and PCA for final factor selection.
\newline

\textbf{IntelliSearch: Unifying Search, Empowering Action for Tool Calling Autonomous Agents}

\url{https://github.com/SJTU-SAI-GeekCenter/IntelliSearch}

Core contributor of \textbf{IntelliSearch}, an MCP-rooted search agent evolved into a decoupled, lightweight infrastructure for the Agentic ecosystem. By unifying context memory, dynamic tool scheduling, and multi-agent communication, it provides developers with a perfectly balanced and adaptable framework.
\newline


\textbf{Open Source \& Community Contributions} \\
\url{https://xiyuanyang-code.github.io} \\ \url{https://sjtu-sai.github.io/SAI-Community/}

Initiator and core contributor of \textbf{SAI Community}, the first student-led high-quality information aggregation forum at SJTU-SAI, fostering knowledge sharing within the academic community. Concurrently, I maintain a \textbf{technical blog} featuring 150+ articles (480k+ words) on computer science and AI, and actively contribute to open source via 30+ GitHub repositories.


\section{Skills}
\textbf{Programming Languages}: Python (Proficient), C++ (Proficient), Rust, JavaScript, HTML, CSS.

\textbf{Tools}: Git, LaTeX, Shell, Docker.

\textbf{Python Modules}: Torch (Proficient), Numpy, Pandas, Matplotlib, BeautifulSoup, FastMCP, etc.

\textbf{ML \& DL}: Familiar with Deep Learning architectures and model training techniques.

\textbf{LLM \& Agents}: Familiar with core architectures for Large Language Models (post training) and agentic frameworks. 

\textbf{Languages}: Chinese (native), English (CET-6: 584).




\section{Awards and Certifications}

\twopartheader{\textbf{Challenge Cup} Competition for "Unveiling the List and Appointing the Best" \textbf{\href{https://mp.weixin.qq.com/s/aO85Qtgv1q-AhClfEu4Gpw}{Defender}}}{2025}


Research Proposal for a General-Purpose AI Assistant Technology Based on Multi-Agent Architecture Competition.
\newline


\twopartheader{\textbf{Honorable Mention in MCM}}{2025}

Honorable Mention, COMAP Mathematical Contest in Modeling / Interdisciplinary Contest in Modeling (MCM/ICM).

2025-C: Models for Olympic Medal Tables.
\newline

\end{document}